\textbf{The Mint Scale: A Fresh Validation of the Multimodal Interoception Questionnaire and Comparison to the MAIA, BPQ and IAS}

### 2025-08-12 paper/manuscript.tex
push

\usepackage[nolongtablepatch]{lineno}
\linenumbers

@@

\keywords{Interoception questionnaire, interoceptive accuracy scale,
MAIA, Mint Validation, Body Awareness}

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Giulia
Poreiro}{0000-0002-2343-5109}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, left=2mm, arc=.35mm, bottomrule=.15mm, leftrule=.75mm, rightrule=.15mm, colback=white, breakable, opacityback=0, colframe=quarto-callout-note-color-frame, toprule=.15mm]

This preprint is a non-peer-reviewed work from the
\href{https://realitybending.github.io/}{\textbf{Reality Bending Lab}}.
\begin{center}
\includegraphics[width=0.2\linewidth,height=\textheight,keepaspectratio]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
\end{center}

@@

\resetlinenumber[1]

@@

Main issues in existing questionnaires:

\begin{itemize}
\tightlist
\item
  Either heavily based on theories (e.g., focusing on specific
  ``alleged'' dimensions), despite shaky evidence for said-theories
\item
  Do not control for context (which leads to variability in
  interpretation and occurence)
\item
  Often quite narrow in the modalities covered (or scattered, like the
  IAS)
\end{itemize}

@@

TODO: write intro.

\begin{itemize}
\tightlist
\item
  Goal of study 1: to generate a lot of items, analyze its structure and
  reduce them to a balanced set of items.
\end{itemize}

@@

After removing redundant items using UVA, we iteratively fitted
hierarchical EGA models (which additionally estimates higher-order
``meta'' clusters) using ``glasso''
(\citeproc{ref-friedman2008sparse}{Friedman et al., 2008}) and the
``Leiden'' algorithm (\citeproc{ref-traag2019louvain}{Traag et al.,
2019}) for community detection, refining the item pool at each step. We
started by removing items with a low (\textless{} 80\%) cluster
stability (i.e., volatile items which jump between clusters across
bootstrapped samples), followed by odd items belonging to no clusters or
pairs of items (i.e., we keep items belonging to clusters of more than 2
items). Finally, for each lower-level cluster, we selected the 3 items
with the highest node centrality (i.e., the highest loading in the
cluster).

@@

\begin{itemize}
\tightlist
\item
  Possible (although not at all significant) bias consistent across
  indices in favour of a greater similarity with the modality-grouping
  condition. Futher research with more data (here we only had
  \textasciitilde200 observation per condition) might be able to yield
  more conclusive results. In general, testing the presentation mode is
  a novel approach which should be more widely applied to psychometric
  validations.
\item
  We grouped some of the dimensions under ``Awareness'', despite being
  similar to items included in the IAS typically conceptualized as
  ``Accuracy''. However, we believe that subjective scales cannot be
  pure measures of accuracy, as they are inherently subjective and thus
  reflect a degree of awareness (of one's accurate noticing or
  sensation).
\item
  Olfactory compensation: pseudo-interoceptive pathway whereby people
  with interoceptive deficits would compensate by gathering evidence
  about their internal state externally (e.g., via smell).
\item
  The metacluster ``Sensitivity'' seems to be grouping iterms related to
  visceropcetion and (hyper)sensitivity (Derm).
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Goal of study 2: to validate the Mint scale against other
  interoception scales.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Structure: Low stability of \emph{Olfa} as belonging in the deficit
  group. More studies are needed to investigate its place and cluster
  invariance: it is possible that its association might depend on other
  factors or categories.
\item
  Main contender is MAIA. But its most sensitive dimensions seem to be
  the least related to interoception, which is dangerous as it might
  lead to findings with associations misattributed to ``Interoception''
  (just because it correlate with some MAIA dimensions), but it might
  have nothing to do with interoception per se and more with emotion
  regulation.
\item
  Basically the pattern is clear: everything high-level, metacognitive
  and highly subjective related to wellbeing and general affective state
  is the most strongly related to the MAIA through some of its Emotion
  regulation dimensions. All the other outcomes actually related to
  interoceptive processes are most strongly predicted by the Mint.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Future directions: needs to test relationship with physiological
  measures of interoception.
\item
  Also, the structure might still require a bit of deeper investigation,
  in particular with some of its facets (\emph{Olfa} and \emph{Derm})
  which might display different associations depending on the context or
  the population.
\end{itemize}

@@

We would like to thank the dissertation students from the University of
Sussex for their help in data collection. DM would also like to thank
\ldots{} for the motivation provided to write this paper.

@@

@@

@@

@@

@@

@@

>>>>

@@

\keywords{Interoception questionnaire, interoceptive accuracy scale,
MAIA, Mint Validation, Body Awareness, Health}

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}\par{\addORCIDlink{Giulia
Poreiro}{0000-0002-2343-5109}} 
\par{ }
\par{     \begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, toprule=.15mm, arc=.35mm, left=2mm, breakable, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, leftrule=.75mm, opacityback=0, colback=white]

This preprint is a non-peer-reviewed work from the
\href{https://realitybending.github.io/}{\textbf{Reality Bending Lab}}.
\includegraphics[width=0.2\linewidth,height=\textheight,keepaspectratio]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}

@@

@@

Interoception - the sensing and interpretation of the body's internal
physiological signals - plays a fundamental role in processes ranging
from homeostatic regulation to emotion, decision-making, and mental
health (\citeproc{ref-craig2002how}{Craig, 2002};
\citeproc{ref-critchley2017interoception}{Critchley \& Garfinkel,
2017}). Despite its growing recognition, the field is hindered by
inconsistent definitions and fragmented measurement approaches
(\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022},
\citeproc{ref-desmedt2025discrepancies}{2025};
\citeproc{ref-khalsa2018interoception}{Khalsa et al., 2018}). Available
tools include ``objective'' physiological tasks (e.g., heartbeat
counting or tracking) and ``subjective'' self-reports, and encompass
both ``explicit'' paradigms that direct participants' attention and
consciousness to internal sensations and ``implicit'' paradigms that do
not (e.g., heartbeat evoked potentials recorded during rest). These
assessments are often targeted at only one of several interoceptive
modalities (e.g., cardioception, respiroception, gastroception), and are
mapped onto theoretical dimensions (e.g., accuracy, sensitivity,
awareness, \citeproc{ref-garfinkel2015knowing}{Garfinkel et al., 2015})
within a rapidly evolving theoretical scaffolding. However, no consensus
exists on a gold-standard measure, and each approach has distinct
limitations: physiological tasks often require specialised equipment and
expertise, are time-consuming, and are challenging to administer at
scale, whereas questionnaires are constrained by their inherent
subjectivity. Crucially, the psychometric quality of many of these
measures is questionable (e.g., see criticism about the heartbeat
counting task, \citeproc{ref-zamariola2018interoceptive}{Zamariola et
al., 2018}), yielding low inter-task correlations
(\citeproc{ref-murphy2018classifying}{Murphy et al., 2018}), raising
serious concerns about their reliability and validity (e.g., measures
presented as measuring one theoretical dimension but likely measuring
something else). This measurement conundrum hinders progress in
comparing, replicating, and interpreting interoception-related findings,
underscoring the need to develop improved tools that align with modern
psychometric standards.

The present work focuses on self-report questionnaires, which offer a
scalable and accessible tool complementing physiological tasks. Among
the numerous questionnaires available, a handful seem to dominate the
literature (\citeproc{ref-desmedt2022measures}{Desmedt et al., 2022}),
including the Body Perception Questionnaire (BPQ,
\citeproc{ref-kolacz2018body}{Kolacz et al., 2018}), the
Multidimensional Assessment of Interoceptive Awareness (MAIA,
\citeproc{ref-mehling2018multidimensional}{Mehling et al., 2018}), and
the Interoceptive Accuracy Scale (IAS,
\citeproc{ref-murphy2018classifying}{Murphy et al., 2018}). These tools
were developed in different eras of a rapidly evolving field, each with
its own objectives and philosophies. The BPQ, one of the earliest
measures, emphasizes the assessment of body awareness and autonomic
nervous system (ANS) reactivity, focusing on subjective experiences of
physiological stress reactions in organs innervated by the ANS, such as
those triggered by stress or trauma
(\citeproc{ref-porges1993body}{\textbf{porges1993body?}}). The MAIA
incorporated ideas from the then-booming emotion regulation and
mindfulness fields, including subscales assessing adaptive coping
strategies and metacognitive insights about the body. By contrast, the
IAS was recently crafted to sidestep such high-level - possibly
tangential - constructs and instead capture subjective reports of
concrete bodily events (e.g., coughing, sneezing) as proxies for
interoceptive accuracy.

These differing philosophies have practical consequences, leading to
poor convergence between scales that are assumed to measure the same
construct (\citeproc{ref-vig2022questionnaires}{Vig et al., 2022}) - a
classic example of the ``jingle fallacy'' where the shared label of
``interoception'' can mask underlying measurand differences, which in
turn hinders replication and theoretical integration. Recent work has
been focused on aligning subjective measures and facets with theoretical
models, debating whether they measure interoceptive ``sensitivity'' or
other dimensions (accuracy, attention, deficits). However, this focus on
a theory-driven approach might be premature when theoretical models are
in flux, and when a topographic mapping to self-report dimensions is not
guaranteed (e.g.~distinctions that are relevant at a neuroanatomical or
cognitive level might not necessarily translate into the same structural
landscape of subjective experiences). More fundamentally, existing
questionnaires suffer from two major structural blind spots. First, they
are often narrow or unsystematic in their coverage of bodily
\emph{modalities}, with a heavy bias towards cardio-respiratory
sensations and a neglect of others like gastric, urogenital, or
thermoregulatory signals. Second, and perhaps most critically, they fail
to control for the \emph{context} in which an interoceptive experience
occurs, introducing significant variability in how participants
interpret and respond to items. For example, an item about ``feeling
your heart beat'' is ambiguous; its frequency, experience and its
interpretation differ vastly depending on whether it occurs during
physical exercise, a moment of anxiety, or quiet rest (e.g., someone who
exercises regularly, or is anxious, might more easily recall an instance
of occurrence of feeling their heart beating and respond based on that
contextual saliency).

To address these gaps, we introduce the Multimodal Interoception
Questionnaire (Mint). The overarching aim of this work is to develop and
validate a new questionnaire that systematically addresses these
limitations. In Study 1, we detail the bottom-up development of the
Mint, using a ``modality-by-context'' framework to generate a
comprehensive item pool, which is then refined using cutting-edge
psychometric network analysis. In Study 2, we validate the final version
of the Mint against the established interoception questionnaires,
demonstrating its robust structure and predictive validity for a range
of clinically-relevant outcomes.

@@

The primary goal of Study 1 was to develop a new interoception
questionnaire by generating a comprehensive item pool and refining it
into a psychometrically robust scale. To overcome the limitations of
existing measures, we adopted a bottom-up, theoretically agnostic
approach. Instead of imposing a pre-defined theoretical structure, we
focused on two tangible and systematically controllable aspects of
interoceptive experience: the \emph{modality} of the sensation and the
\emph{context} in which it occurs. The objective was not to create
\emph{yet another scale} measuring an alleged distinct construct or
variation, but rather to synthesize existing ideas and frameworks into a
comprehensive and modern tool that captures the richness of
interoceptive experiences and encompasses the most relevant facets of
interoception.

Our item generation process was guided by a ``modality-by-context'' grid
designed to overcome the limitations of existing scales. For
\emph{modalities}, we expanded beyond the typical cardio-respiratory
focus to include a broader range of bodily systems: cardiac,
respiratory, gastric, genital, bladder \& colon, and skin \& temperature
(the latter of which being increasingly recognized as a key
interoceptive channel, \citeproc{ref-crucianelli2023role}{Crucianelli \&
Ehrsson, 2023}). We also included a ``general state'' category to
capture the integrated sense of the body's overall physiological
condition (\citeproc{ref-craig2002how}{Craig, 2002};
\citeproc{ref-craig2003interoception}{Craig, 2003}). For
\emph{contexts}, we designed facets to capture specific situational
contexts like negative (anxious) and positive (sexual) arousal, which
reflect distinct bodily states with differing interoceptive signatures,
as well as other experiential qualities tapping into elaboration and
threshold of perception, such as sensitivity, accuracy, and confusion.
To maintain continuity with established work while making targeted
improvements, we purposefully adapted items from existing questionnaires
(e.g., IAS-like items related to observable behaviors). This systematic
framework yielded a diverse pool of 120 initial items, ensuring
comprehensive coverage while minimizing the ambiguity inherent in
context-free questions.

The final step involved a data-driven reduction of this item pool. We
employed cutting-edge psychometric network-based techniques to identify
and remove redundant items and to uncover the most stable and coherent
dimensional structure. Additionally, we designed the study so that we
could explore an often overlooked psychometric quality: the invariance
of the structure to the presentation format (how items are grouped
together on the screen, whether by modality, facet, or randomly)
influences the resulting psychometric structure. This rigorous,
multi-stage process was designed to produce a subset of items with a
clear, stable, and theoretically rich hierarchical structure, ready for
formal validation.

@@

After removing redundant items using UVA, we iteratively fitted
hierarchical EGA models (which additionally estimate higher-order
``meta'' clusters) using ``glasso''
(\citeproc{ref-friedman2008sparse}{Friedman et al., 2008}) and the
``Leiden'' algorithm (\citeproc{ref-traag2019louvain}{Traag et al.,
2019}) for community detection, refining the item pool at each step. We
started by removing items with a low (\textless{} 80\%) cluster
stability (i.e., volatile items which jump between clusters across
bootstrapped samples), followed by odd items belonging to no clusters or
pairs of items (i.e., we keep items belonging to clusters of more than 2
items). Finally, for each lower-level cluster, we selected the 3 items
with the highest node centrality (i.e., the highest loading in the
cluster).

@@

The primary aim of Study 1 was to develop and refine a large,
systematically generated pool of interoceptive items into a
psychometrically sound and structurally coherent questionnaire. Starting
with 120 items derived from a modality-by-context grid, we employed a
multi-step, data-driven reduction process using cutting-edge structure
analysis methods. This rigorous procedure yielded a final, balanced set
of 45 items, organized within a stable hierarchical structure comprising
three higher-order dimensions (Interoceptive Deficits, Interoceptive
Awareness, Interoceptive Sensitivity) and 12 distinct lower-level
facets.

One innovation of this study was to test the effect of item presentation
by comparing structures across different grouping conditions. While the
analysis revealed no significant effect, a consistent (though
non-significant) trend suggested that grouping items by modality may be
slightly more conducive to revealing the underlying psychometric
structure than grouping by facet or randomly. This finding, while
preliminary due to the sample size per condition (\(N \pm 200\)),
highlights a potentially important and under-investigated aspect of
questionnaire design that warrants future research.

The resulting hierarchical structure offers novel yet interpretable
insights into self-reported interoception, with flexible degrees of
granularity. Notably, we categorised several facets (typically related
to objective external behaviours, like coughing or sneezing) under the
label ``Awareness'', that might traditionally be named ``Accuracy'' in
other scales. Our rationale is that subjective self-report, by its very
nature, cannot be a pure measure of objective accuracy, but at best a
proxy of an individual's subjective certainty or awareness of their
interoceptive processes. Furthermore, our bottom-up approach revealed
intriguing facets, such as ``Olfactory Compensation''. This finding
provide further evidence for a pseudo-interoceptive pathway, whereby
individuals with potentially poorer access to internal signals may
compensate by relying on external cues (e.g., odours) to infer their
bodily state. The ``Sensitivity'' metacluster also grouped core
visceroceptive facets (e.g., ``Cardioception'', ``Gastroception'') with
``Dermal Hypersensitivity'', pointing to a potential common dimension of
heightened perceptual sensitivity to bodily sensations.

In summary, Study 1 successfully leveraged a systematic item generation
process and modern analytical techniques to produce a 45-item
questionnaire with a clear, stable, and theoretically rich hierarchical
structure. The next crucial step is to formally validate this new
instrument by examining its psychometric properties and its relationship
with existing measures in a new, independent sample, which is the
objective of Study 2.

@@

Following the generation and selection of a set of 45 interoceptive
items, the next objective is to formally validate this new instrument in
a large, independent sample, a crucial step for establishing the
psychometric soundness and unique contribution of the Mint scale to the
field of interoception research. To this end, we sought to 1) re-assess
the structure of the shorter version and 2) establish its convergent
validity by examining the correlations with other established and
popular interoception questionnaires (namely the MAIA-2, BPQ, and IAS),
as well as other related measures (e.g., alexithymia). Finally, we
assessed its criterion validity by directly comparing the predictive
power of the interoceptive scales across a broad range of outcomes,
including emotional, cognitive, and clinical variables.

@@

The primary goal of Study 2 was to validate the items selected in Study
1. This involved re-assessing its structure in a new, large sample, and
establishing its convergent and criterion validity against other
established interoception questionnaires. The analysis led to a final,
refined 33-item Mint scale with a stable and theoretically coherent
hierarchical structure, which demonstrated substantial predictive power
across a range of outcomes.

Re-validating the structure after item selection is a crucial step in
questionnaire development. When a large item pool is reduced, the
context changes, which can alter the perceived meaning and relationships
between the remaining items. For instance, a questionnaire with many
items suggesting abnormality or pathology might colour other neutral
items with a negative connotation. While the original structure was
mostly replicated, the re-validation allowed for a clarification of some
of the higher-order dimensions (for instance, the ``Sensitivity''
metacluster became more clearly defined around core interoceptive
clusters). The final structure, comprising 11 facets and 3 metaclusters,
showed excellent structural consistency and stability, providing a solid
foundation for the scale. However, the \emph{Olfa} (Olfactory
Compensation) cluster showed lower stability in its placement within the
\emph{Deficit} metacluster. This suggests its role may be more complex,
and future studies are needed to investigate its place and invariance
across different populations and contexts.

The criterion validity analysis revealed a clear and compelling pattern
of results. The Mint scale, particularly its \emph{Deficit} metacluster,
consistently outperformed other scales in predicting outcomes directly
related to alterations in bodily experience and self-regulation, such as
alexithymia, dissociative experiences, ADHD, autism, and various somatic
symptoms. The main contender, the MAIA-2, showed an advantage primarily
for outcomes related to general well-being, such as life satisfaction,
depression, and anxiety. However, this advantage was almost entirely
driven by dimensions highly related to emotion regulation abilities,
namely \emph{Trusting} and \emph{Not-Worrying}, whose inclusion as core
interoceptive facets has been questioned
(\citeproc{ref-ferentzi2021examining}{Ferentzi et al., 2021}). When
these dimensions were removed (in the \emph{iMAIA} version), the
MAIA-2's predictive power for these outcomes dropped considerably, often
below that of the Mint.

This highlights a crucial issue in the field: the potential for
misattributing findings to ``interoception'' when they may be driven by
broader emotion regulation capacities
(\citeproc{ref-murphy2020testing}{Murphy et al., 2020}). While valuable,
the MAIA-2's most predictive subscales appear less related to core
interoceptive processing and more to metacognitive beliefs about one's
body and emotional coping. The Mint, in contrast, appears to tap more
directly into distinct facets of interoceptive experience, from visceral
sensitivity to perceived deficits. The pattern is clear: for high-level,
metacognitive aspects of affective state and well-being, the MAIA-2's
emotion regulation facets are highly relevant. For outcomes tied more
specifically to bodily processes, clinical conditions characterized by
sensory dysregulation, and nuanced interoceptive experiences, the Mint
offers superior predictive validity and specificity.

@@

Across two studies, we developed and validated the Multimodal
Interoception Questionnaire (Mint), a new 33-item self-report measure of
interoception. Our approach addressed key limitations of existing scales
by starting with a systematically generated, broad item pool that
explicitly controlled for context and modality, and then using a
data-driven reduction process. The result is a psychometrically robust
instrument with a stable, hierarchical structure comprising three
higher-order metaclusters, namely \emph{Interoceptive Deficit},
\emph{Interoceptive Awareness}, and \emph{Visceroception}, and 11
distinct lower-level facets. The validation study demonstrated that the
Mint not only captures variance present in other popular scales (MAIA-2,
BPQ and IAS) but also offers superior predictive power for a range of
clinical and cognitive outcomes, particularly those tied to altered
bodily perception.

A key contribution of the Mint is its potential ability to disentangle
core interoceptive experiences from more general emotion regulation
capacities. Our findings show that while the MAIA-2 is a potent
predictor of general well-being, this is largely driven by its
\emph{Trusting} and \emph{Not-Worrying} subscales, which heavily tap
into emotion regulation skills and coping strategies. The Mint,
conversely, excelled at predicting conditions like alexithymia, ADHD,
autism, and somatic symptoms, where alterations in bodily sensing are a
core feature. This suggests the Mint provides a more specific measure of
interoceptive processing, offering researchers a finer-grained tool to
probe the role of bodily awareness in health and disease.

Despite these strengths, the present work has limitations that open
avenues for future research. First, as a self-report measure, the Mint
captures subjective beliefs about interoceptive abilities, not objective
accuracy. A crucial next step is to investigate the relationship between
Mint scores and physiological or behavioural measures of interoception
(e.g., heartbeat tracking tasks, heartbeat evoked potentials). This
would help establish the extent to which subjective reports on the Mint
correspond to objective interoceptive performance. Future research could
also systematically examine the cost of shorter versions, by
investigating the tradeoffs incurred by versions with only the one or
two most central facets per metacluster and their impact on psychometric
qualities and predictive power.

While the overall structure of the Mint is stable, some facets warrant
deeper investigation. The \emph{Olfa} (Olfactory Compensation) and
\emph{Derm} (Dermal Hypersensitivity) clusters, for instance, showed
more complex patterns of association. Their placement within the
\emph{Deficit} metacluster is theoretically intriguing but requires
further validation. The former aligns with predictive coding models
suggesting that individuals may rely on exteroceptive cues (like odours)
to infer internal states (\citeproc{ref-paulus2010interoception}{Paulus
\& Stein, 2010}), a form of pseudo-interoception (or
extero-interoception). The latter points to a potential link between
visceral and cutaneous sensitivity, possibly reflecting a general trait
of heightened bodily awareness or a shared mechanism of central
sensitization, which has been observed in conditions like chronic pain
(\citeproc{ref-di2016alexithymia}{Di Tella \& Castelli, 2016}). Future
studies should examine the invariance of the Mint's structure across
different populations (e.g., clinical vs.~non-clinical groups) and
contexts (e.g., heightened arousal vs.~rest) to clarify the role of
these more nuanced facets. Such work could reveal whether their
relevance and pattern of associations differs in conditions like anxiety
disorders, chronic pain, or neurodevelopmental disorders.

In conclusion, the Mint scale represents a significant methodological
advancement for the field of interoception research. By providing a
validated, structurally coherent, and nuanced tool, it allows for a more
precise assessment of self-reported interoceptive experiences. Its
various forms (full, meta, mini, and micro) offer flexibility for
researchers and clinicians, paving the way for a deeper understanding of
the multifaceted role of interoception in human psychology and
pathophysiology.

@@

We would like to thank the dissertation students from the University of
Sussex for their help in data collection. DM would also like to thank
Anastasia for the motivation provided to write this paper.

@@

\bibitem[\citeproctext]{ref-craig2002how}
Craig, A. D. (2002). How do you feel? Interoception: The sense of the
physiological condition of the body. \emph{Nature Reviews Neuroscience},
\emph{3}(8), 655--666. \url{https://doi.org/10.1038/nrn894}

\bibitem[\citeproctext]{ref-craig2003interoception}
Craig, A. D. (2003). Interoception: The sense of the physiological
condition of the body. \emph{Current Opinion in Neurobiology},
\emph{13}(4), 500--505.

\bibitem[\citeproctext]{ref-critchley2017interoception}
Critchley, H. D., \& Garfinkel, S. N. (2017). Interoception and emotion.
\emph{Current Opinion in Psychology}, \emph{17}, 7--14.
\url{https://doi.org/10.1016/j.copsyc.2017.04.020}

\bibitem[\citeproctext]{ref-crucianelli2023role}
Crucianelli, L., \& Ehrsson, H. H. (2023). The role of the skin in
interoception: A neglected organ? \emph{Perspectives on Psychological
Science}, \emph{18}(1), 224--238.

@@

\bibitem[\citeproctext]{ref-desmedt2022measures}
Desmedt, O., Heeren, A., Corneille, O., \& Luminet, O. (2022). What do
measures of self-report interoception measure? Insights from a
systematic review, latent factor analysis, and network approach.
\emph{Biological Psychology}, \emph{169}, 108289.

\bibitem[\citeproctext]{ref-desmedt2025discrepancies}
Desmedt, O., Luminet, O., Maurage, P., \& Corneille, O. (2025).
Discrepancies in the definition and measurement of human interoception:
A comprehensive discussion and suggested ways forward.
\emph{Perspectives on Psychological Science}, \emph{20}(1), 76--98.

\bibitem[\citeproctext]{ref-di2016alexithymia}
Di Tella, M., \& Castelli, L. (2016). Alexithymia in chronic pain
disorders. \emph{Current Rheumatology Reports}, \emph{18}(7), 41.

@@

\bibitem[\citeproctext]{ref-garfinkel2015knowing}
Garfinkel, S. N., Seth, A. K., Barrett, A. B., Suzuki, K., \& Critchley,
H. D. (2015). Knowing your own heart: Distinguishing interoceptive
accuracy from interoceptive awareness. \emph{Biological Psychology},
\emph{104}, 65--74.
\url{https://doi.org/10.1016/j.biopsycho.2014.11.004}

@@

\bibitem[\citeproctext]{ref-khalsa2018interoception}
Khalsa, S. S., Adolphs, R., Cameron, O. G., Critchley, H. D., Davenport,
P. W., Feinstein, J. S., \& Zucker, N. (2018). Interoception and mental
health: A roadmap. \emph{Biological Psychiatry: Cognitive Neuroscience
and Neuroimaging}, \emph{3}(6), 501--513.
\url{https://doi.org/10.1016/j.bpsc.2017.12.004}

\bibitem[\citeproctext]{ref-kolacz2018body}
Kolacz, J., Holmes, L., \& Porges, S. W. (2018). Body perception
questionnaire (BPQ) manual. \emph{Traumatic Stress Research Consortium}.

@@

\bibitem[\citeproctext]{ref-murphy2018classifying}
Murphy, J., Catmur, C., \& Bird, G. (2018). Classifying individual
differences in interoception: Implications for the measurement of
interoceptive accuracy. \emph{Psychonomic Bulletin \& Review},
\emph{25}(4), 1424--1431.
\url{https://doi.org/10.3758/s13423-017-1339-z}

\bibitem[\citeproctext]{ref-paulus2010interoception}
Paulus, M. P., \& Stein, M. B. (2010). Interoception in anxiety and
depression. \emph{Brain Structure and Function}, \emph{214}(5),
451--463.

@@

\bibitem[\citeproctext]{ref-vig2022questionnaires}
Vig, L., Köteles, F., \& Ferentzi, E. (2022). Questionnaires of
interoception do not assess the same construct. \emph{PLoS One},
\emph{17}(8), e0273299.

\bibitem[\citeproctext]{ref-zamariola2018interoceptive}
Zamariola, G., Maurage, P., Luminet, O., \& Corneille, O. (2018).
Interoceptive accuracy scores from the heartbeat counting task are
problematic: Evidence from simple bivariate correlations.
\emph{Biological Psychology}, \emph{137}, 12--17.
